\chapter{Software Architecture Design}
\label{chap:software-architecture-design}

\raggedright
\section{System Architecture Overview}
\label{section:architecture-overview}
<TIP: Provide a high-level description of your system's structure.
Include either a Domain Model (to describe core business concepts
and their relationships)
or a Design Class Diagram (to describe how your code is organized
into classes and packages),
whichever best communicates your design.
Accompany your diagram with a short paragraph explaining the key
components and how they interact. />

\raggedright
\section{Software Design}
\label{section:software-design}
<TIP: Describe the runtime behavior of your system.
Include a Sequence Diagram for your most important use cases.
Focus on scenarios with non-trivial interactions between components.
If your project involves a novel algorithm,
describe it here and explain why you designed it this way. />

\pagebreak

\raggedright
\section{AI and Data Design}
\label{section:ai-data-design}
\raggedright
\subsection{Data Sources and Collection}
{
    \setlength{\parindent}{2em}
    This project will utilize publicly available datasets to train and evaluate the AI components. 
    \vspace{1em}
    \\The primary data sources include:
    \begin{itemize}
        \item \textbf{AMI Meeting Corpus}: Provides over 170 annotated meeting recordings along with transcripts, allowing the system to learn realistic meeting conversations and structures. 
        \item \textbf{TIAGE dataset}: Used for topic drift detection, containing approximately 500 text samples focused on conversational topic classification.
    \end{itemize}
}

\subsection{Model Design}
{
    \setlength{\parindent}{2em}
    The system adopts a modular approach by integrating multiple AI models, each designed for a specific task within the meeting workflow.
    \\[1em]For speech-to-text transcription, \textbf{WhisperX} is used due to its strong performance in real-time transcription and multilingual support. 
    The model will convert spoken audio into text, which serves as the foundation for further processing.
    \\[1em]For question answering, a \textbf{BERT-based model (BertQA)} is used. 
    This model is effective at extracting precise answers from contextual data. 
    It is integrated into an agentic system that retrieves relevant information from past meetings and generates context-aware responses.
    \\[1em]For text summarization, the system will utilize \textbf{BART} for its strong performance in generating concise and meaningful summaries from long meeting transcripts.
    \\[1em]For task management, the \textbf{LLaMA 3} will be used to identify and extract actionable tasks from meeting content. This model can detect responsibilities, deadlines, and action items from natural language.
    \\[1em]All models are integrated into a pipeline where outputs from one component are used as inputs for others. 
    For example, transcription feeds into summarization and question answering. 
    Prompt engineering techniques are applied when interacting with large language models to ensure consistent and relevant outputs.
    The selected models are chosen based on their effectiveness in natural language processing tasks and their ability to handle real-time conversational data.
}
\subsection{Evaluation}
{
    \setlength{\parindent}{2em}
    The performance of the AI components is evaluated using task-specific metrics.
    \\[1em]For topic drift detection, \textbf{BERTScore} is used to measure the semantic similarity between sentences, allowing the system to detect when a conversation deviates from the main topic.
    \\[1em]For speech-to-text transcription, \textbf{Word Error Rate (WER)} is used to evaluate the accuracy of the generated transcript compared to the ground truth.
    \\[1em]For the question answering component, evaluation includes \textbf{task success rate, correctness, and human evaluation}. These metrics assess how well the system retrieves and presents relevant information.
    \\[1em]For text summarization, \textbf{ROUGE} metrics are used, including \textbf{ROUGE-N} and \textbf{ROUGE-L}. These measure the overlap between generated summaries and reference summaries in terms of precision, recall, and sequence similarity.
    \\[1em]For task management, standard classification metrics such as \textbf{accuracy, precision, recall, and F1-score} are used. These are calculated using K-fold cross-validation to ensure the model performs consistently across different data splits.
    \\[1em]Together, these evaluation metrics provide a comprehensive assessment of the system's performance across all AI components.
}